### 2021-06-08 thesis/tex/introduction.tex
update

To make matters even worse, three of the massless particles in the Standard Model do have mass.
In this thesis we focus on the said particles, the neutrinos, and propose extensions to the Standard Model
related to the neutrinos. We then compare the effects of these extensions with collected data to see 
if our new theory more closely describes Nature or not.

@@

In Chapter~\ref{ch:ic}, we present an experimental procedure which can be used to observe signals from neutrinos originating
from cosmic ray interactions in the atmosphere of the Earth. Furthermore, we introduce the reader to 
the two present Antarctic neutrino detectors: IceCube and DeepCore. We also give a brief summary 
about a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which 
we will use as a forecast in our analysis.

>>>>

To make matters even worse, three of the massless particles in the Standard Model do have mass.
In this thesis we focus on the said particles, the neutrinos, and propose extensions to the Standard Model
related to them. We then compare the effects of these extensions with collected data to see 
if our new theory more closely describes Nature or not.

@@

In Chapter~\ref{ch:ic}, we present an experimental procedure used to observe signals from neutrinos originating
from cosmic ray interactions in the atmosphere of the Earth. Furthermore, we introduce the reader to 
the two present Antarctic neutrino detectors: IceCube and DeepCore. We also give a brief summary 
about a proposed detector upgrade: Precision IceCube Next Generation Upgrade (PINGU), which 
we will use as a forecast in our analysis.

### 2021-06-08 thesis/tex/oscillations.tex
update

We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa Lagrangian 
\begin{align}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,.
\end{align}
Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, with the former resulting in the charged lepton masses being non-definite. This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$.
Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, since no flavor rotation can make massless fields massive.

\begin{align}
    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
\end{align}
Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.
While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. 
This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement of neutrino flavor eigenstates to have a definite mass. 
The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
This fact is introduced as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.

>>>>

We extend the Standard Model by adding a right-handed component of this field with neutrino Yukawa couplings $Y_{\alpha \beta}^{\prime \nu}$ to the Higgs-lepton Yukawa Lagrangian 
\begin{align}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]\,.
\end{align}
Now, the Yukawa coupling matrices $Y^{\prime \ell}$ and $Y^{\prime \nu}$ are non-diagonal, with the former resulting in the charged lepton masses being non-definite. 
This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$ as
\begin{align}
    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
\end{align}
Similarily, we diagonalize and $Y^{\prime \nu}$ with a unitary matrix $V^\nu$. We note that this will not yet generate neutrino masses, since no flavor rotation can make massless fields massive.
Now we state a crucial difference between the properties of the charged lepton and the neutrino fields.
While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. 
This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement of neutrino flavor eigenstates to have a definite mass. 
The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. 
This fact is introduced as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.
